% SVN Info:
% $Date: 2020-11-25 15:16:56 +0100 (Mi, 25 Nov 2020) $
% $Rev: 5261 $
% $Author: kolja $
\section{Information Required by DIN EN 61010-1}
\subsection{Manufacturer\label{cp:manu}}

The Ndigo5G is a product of:\

\begin{quote}
    cronologic GmbH \& Co. KG\\
    Jahnstraße 49\\
    60318 Frankfurt\par
    \noindent HRA 42869 beim Amtsgericht Frankfurt/M\par
    \noindent VAT-ID: DE235184378
\end{quote}

\subsection{Intended Use and System Integration}

    The devices are not ready to use as delivered by cronologic. It requires the development of specialized software to fulfill the application of the end user. The device is provided to system integrators to be built into measurement systems that are distributed to end users. These systems usually consist of a Ndigo5G, a main board, a case, application software and possible additional electronics to attach the system to some type of detector. They might also be integrated with the detector.\par

    The Ndigo5G is designed to comply with DIN EN 61326-1 when operated on a PCIe compliant main board housed in a properly shielded enclosure. When operated in a closed standard compliant PC enclosure the device does not pose any hazards as defined by EN 61010-1.\par

    Radiated emissions, noise immunity and safety highly depend on the quality of the enclosure. It is the responsibility of the system integrator to ensure that the assembled system is compliant to applicable standards of the country that the system is operated in, especially regarding user safety and electromagnetic interference. Compliance was only tested for attached cables shorter than 3\,m.\par

    When handling the board, adequate measures have to be taken to protect the circuits against electrostatic discharge (ESD). All power supplied to the system must be turned off before installing the board.

\subsection{Cooling}

    The Ndigo5G in its base configuration has passive cooling that requires a certain amount of air flow. If the case design can't provide enough air flow to the board, a slot cooler like Zalman ZM-SC100 can be placed next to the board. Active cooling is also available as an option to the board.

\subsection{Environmental Conditions}
    See Sections~\ref{enviro_op} and \ref{enviro_store}.

\subsection{Inputs}

    All inputs are AC coupled. The inputs have very high input bandwidth requirements and therefore there are no circuits that provide overvoltage protection for these signals. Any voltage on the inputs above 5\,V or below $-5$\,V relative to the voltage of the slot cover can result in permanent damage to the board.

\subsection{Known Bugs}

\subsubsection{Thunderbolt}
The Ndigo5G does not work in most Thunderbolt PCIe extension enclosures. The reason is unknown.\par
Workarounds:
\begin{itemize}
    \item Use the Ndigo6G. All other cronologic products work reliably in Thunderbolt enclosures. The Ndigo6G offers very similar functionality to the Ndigo5G at a higher performance.$^1$
    \item Use the Ndigo Crate. Electrically, the setup is similar to an external Thunderbolt enclosure.$^2$ 
\end{itemize}

\subsubsection{PCIe 5.0}
The Ndigo5G might not work in PCIe 5.0 slots that support the ``Enhanced Link Behavior Control'' feature.\par
Workarounds:
\begin{itemize}
    \item Disable ``Enhanced Link Behavior Control'' in BIOS.
    \item Limit PCIe transfer rates to transfer rates of up to PCIe 4.
    \item If your main board has PCIe slots that are not PCIe 5.0, install your Ndigo5G in these.
    \item Use Ndigo6G. The Ndigo6G works reliably in PCIe 5.0 slots while offering similar functionality.$^1$
    \item Use the Ndigo Crate.$^2$
\end{itemize}
{\small $^1$\,When using the Ndigo6G as a replacement, there are some software changes required in the device configuration. The readout data format and API is identical. See \href{https://www.cronologic.de/products/adcs/ndigo6g-12}{www.cronologic.de/products/adcs/ndigo6g-12} for details.}\\
{\small $^2$\,Up to eight Ndigo5G can be used in an Ndigo Crate connected to a PC. The PC must have a vacant PCIe slot. See \href{https://www.cronologic.de/products/pcie/pcie-crates}{www.cronologic.de/products/pcie/pcie-crates} for details.}


\subsection{Recycling}

    cronologic is registered with the ``Stiftung Elektro-Altgeräte Register'' as a manufacturer of electronic systems with Registration ID DE 77895909.\par

    The Ndigo5G belongs to category 9, ``Überwachungs und Kontrollinstrumente f\"u{}r aus\-schlie\ss lich gewerbliche Nutzung.'' The last owner of an Ndigo5G must recycle it, treat the board in compliance with \S{}11 and \S{}12 of the German ElektroG, or return it to the manufacturer's address listed on page \pageref{cp:manu}.

\subsection{Export Control}
The Ndigo5G product line is a dual use item under \href{https://eur-lex.europa.eu/eli/reg/2009/428/oj}{Council Regulation (EC) No 428/2009 of 5 May 2009} in section 3A002h. Similar regulations exist in many countries outside Europe.

Regardless of the fact that we at cronologic exclude the use of our products for military purposes, \textbf{the laws of the EU and many other countries restrict exports} of dual-use items. Since we have to apply for a \textbf{General Export Permit} for these countries, delivery processes may be delayed or delivery to certain countries may become impossible.

For the application of this \href{https://www.cronologic.de/faq/export-license}{export license}, we need the following
documtents from you:

\begin{itemize}
    \item Exporter declaration
    \item Company profile
    \item Import license (country dependent)
\end{itemize}

There are countries for which a \textbf{General Export License} can be used for the export of dual-use goods. In this case we need the corresponding documents from you and there will be no further delay. These include:
\begin{itemize}
    \item Australia
    \item Japan
    \item Canada
    \item Liechtenstein
    \item New Zealand
    \item Norway
    \item Switzerland
    \item Singapore
    \item USA
\end{itemize}

Before re-exporting an Ndigo5G or any product containing an Ndigo5G as a 
component, please check you local regulations whether an export permit is 
required.

It is not permitted to export an Ndigo5G to the Russian Federation or the 
Republic of Belarus.